Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-09-05 sections/3algebras.tex
minor.

\begin{theorem}[Additivity]\label{thm:exp_of_products_lc}
    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
    \end{equation}
    %
    between the tensor product of $\infty$-operads $\disk_{/M}$ and $\disk_{/N}$ and the $\infty$-operad $\disk_{/M \times N}$. In particular, there is an equivalence of $\infty$-categories of algebras
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)),
    \end{equation}
    which can be seen to be induced by the functor $\bar{\pi}$.
\end{theorem}

@@

\begin{proof}
    Following \cite[\S.2.2.5]{lurie_ha} the tensor product of $\infty$-operads is defined through a universal property. Namely, we define a bifunctor of $\infty$-operads to be a map $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}$ such that:
    %
    \begin{enumerate}
        \item The diagram
        %
        \begin{equation}
            \begin{tikzcd}
                \mathscr{O}_1 \times \mathscr{O}_2 \arrow[r, "f"] \arrow[d] & \mathscr{O} \arrow[d] \\
                \mathsf{Fin}_* \times \mathsf{Fin}_* \arrow[r, "\wedge"] & \mathsf{Fin}_*
            \end{tikzcd}
        \end{equation}
        %
        commutes, and
        \item $f$ sends pairs of inert morphisms in $\mathscr{O}_1$ and $\mathscr{O}_2$ to inert morphisms in $\mathscr{O}$.
    \end{enumerate}
    %
    We denote the full $\infty$-subcategory of $\mathsf{Fun}_{\mathsf{Fin}_*}(\mathscr{O}_1 \times \mathscr{O}_2, \mathscr{O})$ consisting of the bifunctors of $\infty$-operads by $\mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O})$. The universal property of the tensor product is then that it is the $\infty$-operad $\mathscr{O}_1 \otimes \mathscr{O}_2$ together with a bifunctor of $\infty$-operads $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}_1 \otimes \mathscr{O}_2$ such that composition with $f$ determines an equivalence
    %
    \begin{equation}
        \alg{\mathscr{O}_1 \otimes \mathscr{O}_2} (\mathscr{O}) \xrightarrow{\ \ \simeq \ \ } \mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_1; \mathscr{O}),
    \end{equation}
    %
    for every $\infty$-operad $\mathscr{O}$\footnote{More details about the construction, its existence, and the fact that it captures a nontrivial concept can be found in the provided reference.}.

@@

    To get the data of (2) (..... reduce to $\bsc$). So we need to provide an equivalence of $\infty$-categories
    %
    \begin{equation}\label{eq:b/M_x_b/N=b/MxN}
        \bsc_{/M} \times \bsc_{/N} \xrightarrow[\ \ \simeq \ \ ]{\times} \bsc_{/M \times N}.
    \end{equation}

    To get (1), we remember that as an $\infty$-operad $\disk(\bsc)$ is, in fact, the free symmetric monoidal $\infty$-category generated by $\bsc$, thus it suffices to provide and equivalence of $\infty$-categories
    %
    \begin{equation}
        \bsc \times \bsc \xrightarrow[\ \ \simeq \ \ ]{\times} \bsc.
    \end{equation}
    %
    Remembering that $\bsc$ has a terminal object $*$ so that $\bsc_{/*} \simeq \bsc$, this equivalence is just a special case of \Cref{eq:b/M_x_b/N=b/MxN} in the case when $M = N = *$.

@@

    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies and equivalence at the level of $\alg{\disk_{/M}}$, which together with \Cref{thm:disk_alg=lcfa} this the equivalence of factorization algebras of the statement. That this is related to the functor $\bar{\pi}$ can be seen by inspection of the objects and morphisms.
\end{proof}

>>>>

\begin{theorem}[Additivity]\label{thm:additivity_lc}
    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
    \end{equation}
    %
    between the tensor product of $\infty$-operads $\disk_{/M}$ and $\disk_{/N}$ and the $\infty$-operad $\disk_{/M \times N}$. In particular, there is an equivalence of $\infty$-categories of algebras
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)),
    \end{equation}
    which can be seen to be induced by the functor $\bar{\pi}$.
\end{theorem}

@@

\begin{proof}
    Following \cite[\S.2.2.5]{lurie_ha} the tensor product of $\infty$-operads is defined through a universal property. Namely, we define a bifunctor of $\infty$-operads to be a map $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}$ such that:
    %
    \begin{enumerate}
        \item The diagram
        %
        \begin{equation}
            \begin{tikzcd}
                \mathscr{O}_1 \times \mathscr{O}_2 \arrow[r, "f"] \arrow[d] & \mathscr{O} \arrow[d] \\
                \mathsf{Fin}_* \times \mathsf{Fin}_* \arrow[r, "\wedge"] & \mathsf{Fin}_*
            \end{tikzcd}
        \end{equation}
        %
        commutes, and
        \item $f$ sends pairs of inert morphisms in $\mathscr{O}_1$ and $\mathscr{O}_2$ to inert morphisms in $\mathscr{O}$.
    \end{enumerate}
    %
    We denote the full $\infty$-subcategory of $\mathsf{Fun}_{\mathsf{Fin}_*}(\mathscr{O}_1 \times \mathscr{O}_2, \mathscr{O})$ consisting of the bifunctors of $\infty$-operads by $\mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O})$. The universal property of the tensor product is then that it is the $\infty$-operad $\mathscr{O}_1 \otimes \mathscr{O}_2$ together with a bifunctor of $\infty$-operads $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}_1 \otimes \mathscr{O}_2$ such that composition with $f$ determines an equivalence
    %
    \begin{equation}
        \alg{\mathscr{O}_1 \otimes \mathscr{O}_2} (\mathscr{O}) \xrightarrow{\ \ \simeq \ \ } \mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O}),
    \end{equation}
    %
    for every $\infty$-operad $\mathscr{O}$\footnote{More details about the construction, its existence, and the fact that it captures a nontrivial concept can be found in the provided reference.}.

@@

    To get the data of (2) (..... reduce to $\bsc$). So we need to provide an equivalence of $\infty$-categories
    %
    \begin{equation}\label{eq:b/M_x_b/N=b/MxN}
        \bsc_{/M} \times \bsc_{/N} \xrightarrow{\times} \bsc_{/M \times N}.
    \end{equation}

    To get (1), we remember that as an $\infty$-operad $\disk(\bsc)$ is, in fact, the free symmetric monoidal $\infty$-category generated by $\bsc$, thus it suffices to provide an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bsc \times \bsc \xrightarrow[\ \ \simeq \ \ ]{\times} \bsc.
    \end{equation}
    %
    Remembering that $\bsc$ has a terminal object $*$ so that $\bsc_{/*} \simeq \bsc$, this equivalence is just a special case of \Cref{eq:b/M_x_b/N=b/MxN} in the case when $M = N = *$.

@@

    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies an equivalence at the level of $\alg{\disk_{/M}}$, which together with \Cref{thm:disk_alg=lcfa} gives rise to the equivalence of factorization algebras in the theorem statement. That this is related to the functor $\bar{\pi}$ can be seen by inspection of the objects and morphisms.
\end{proof}
